\thetitle

### 2020-07-08 writing/discussion.tex
many types is a threat to validity

\section{What We Learned}

@@

	  \item is the rational programmer rational?

@@

>>>>

%% -----------------------------------------------------------------------------
\section{What We Learned}

@@

@@

Our setup hides the type choice a rational programmer must make. When the
run-time checks signal an impedance mismatch in the real world, a programmer
does not have a typed component ready to swap in. Instead, the programmer must
come up with the next set of types---and this means the programmer must make
choices. It is normally possible to assign consistent types to variables in a
component in different ways. The creation and curation of the benchmarks over
many years has driven home this lesson, but fortunately, it has also shown that
the types are in most cases reasonably canonical.  We therefore conjecture that
a rational programmer would in most cases come up with an equivalent type
assignment for trail extension as our experimental setup describes.
